\documentclass[a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{biblatex}
\usepackage{graphicx}
\usepackage{acronym}
\usepackage{indentfirst}
\usepackage{longtable}
\usepackage[none]{hyphenat} %stops word separation on new line
\addbibresource{references.bib}

\begin{document}
\include{frontpage}
\tableofcontents
\newpage
\listoffigures
\newpage
\listoftables
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\section{Introduction}

    \subsection{Purpose}
    
    \subsection{Scope and Audience}
        \subsubsection{Description of the problem}
        
        \subsubsection{Description of the system}
        
        \subsubsection{Goals}
    
    \subsection{Document Overview}
    
    \subsection{References}
        \printbibliography
    
    \subsection{Definition, Acronyms and  Abbreviations}
            
            \subsubsection{Definition of Terms}
                \begin{itemize}
                    \item \textbf{User}
                    \item \textbf{Individual}
                    \item \textbf{Third-Party}
                    \item \textbf{Organizer}
                    \item \textbf{Athlete}
                    \item \textbf{Spectator}
                    \item \textbf{TrackMe} the \lq\lq system to be\rq\rq
                    \item \textbf{Credential}
                \end{itemize}
            \subsubsection{Abbreviations}
            
            \subsubsection{Acronyms}
            \begin{acronym}
                \acro{SSN}{Social Security Number}
                \acro{FC}{Fiscal Code}
                \acro{VAT}{Value Added Tax}
            \end{acronym}
            
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\section{Overall Description}

    \subsection{Product Perspective}
    
    \subsection{Product Functions}
    
        \subsubsection{Data4Help}
        
        \subsubsection{Automated-SOS}
        
        \subsubsection{Track4Run}
    
    \subsection{User Characteristics}
    
        \subsubsection{Individual}
        
        \subsubsection{Third-Party}
        
        \subsubsection{Organizer}
        
        \subsubsection{Athlete}
        
        \subsubsection{Spectator}
        
    \subsection{Assumptions, Dependencies and Constraints}
    
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\section{Specific Requirements}

    \subsection{External Interface Requirements}
        
        \subsubsection{User Interfaces}
        
        \subsubsection{Hardware Interfaces}
        
        \subsubsection{Software Interfaces}
        
        \subsubsection{Communication Interfaces}
    
    \subsection{Functional Requirements}
    
        \subsubsection{Registration}
        \textit{TrackMe} must provide a registration interface for both \textit{individual} and \textit{third-party} users.
        
        An \textit{individual} must provide his/her SSN (Social Security Number) or FC (Fiscal Code) during the registration phase in order to be uniquely identified by \textit{TrackMe} application. In this way, the user is also accepting terms of service and allows \textit{TrackMe} to acquire his/her personal data.
        %use cases table structure
        \begin{longtable}{|p{3cm}|p{8cm}|}
        \endhead
        \caption{\fontsize{10px}{0mm}\selectfont Use Case 1: Individual User Registration}\\
        \endlastfoot
            \hline
            \textbf{Name} & Individual User Registration \\
            \hline
            \textbf{Brief Description} & An individual sign up to the application to become an user. \\
            \hline
            \textbf{Actor} & Individual, TrackMe. \\
            \hline
            \textbf{Pre Conditions} & The individual has a valid SSN/FC and he's on the main page. \\
            \hline
            \textbf{Basic Flow} &
            \begin{enumerate}
                \setlength{\itemsep}{0pt}
                \item The individual presses a register button.
                \item TrackMe asks if user is an Individual or a Third Party. The user can choose between these two options.
                \item The individual choose the Individual option.
                \item TrackMe asks to provide a SSN/FC (based on region) and user personal information such as name, age, gender, nationality and optional notes about his health condition.
                \item The individual fills out the requested information and presses the confirm button.
                \item TrackMe registers that user as an Individual User and adds it to the User Database. 
            \end{enumerate} \\
            \hline
            \textbf{Post Conditions} & The individual is successfully registered as an Individual User. \\
            \hline
        \end{longtable}
        
        A \textit{third-party} must provide a \lq\lq VAT number\rq\rq during the registration in order to allow \textit{TrackMe} to check that the submitted VAT is registered and that is issued by an EU Member State.
        \subsubsection{Log-in}
         
        \subsubsection{Log-in Management}
        
        \subsubsection{Connection of External Devices}
        
        \subsubsection{Data4Help Request}
        
        \subsubsection{Data4Help Request Management}
        
        \subsubsection{Automated-SOS Request}
        
        \subsubsection{Automated-SOS Data Management}
        
        \subsubsection{Automated-SOS Request Management}
        
        \subsubsection{Automated-SOS Data Synchronization}
        
        \subsubsection{Run Creation}
        
        \subsubsection{Run Enrollment}
        
        \subsubsection{Run Watching}
        
        \subsubsection{Run Management}
        
    \subsection{Performance Requirements}
    
    \subsection{Design Constraints}
    
        \subsubsection{Standards Compliance}
        
        \subsubsection{Hardware Limitations}
        
        \subsubsection{Other Constraints}
    
    \subsection{Software System Attributes}
        
        \subsubsection{Reliability}
        
        \subsubsection{Availability}
        
        \subsubsection{Security}
        
        \subsubsection{Maintainability}
        
        \subsubsection{Portability}
        
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\section{Formal Analysis using Alloy}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\section{Effort Spent}
    \begin{itemize}
        \item[-] \textbf{Davide Rutigliano:}
        
        \item[-] \textbf{Davide Matta:}
        
        \item[-] \textbf{Claudio Ferrante:}
    \end{itemize}

\end{document}
